---
title: "Standardize chords"
output: html_notebook
---
```{r}
head(all.chord)
```

```{r}
table(tonic)
# tonic
#   A  Ab   B  Bb   C  *C#  Cb???   D  Db   E  Eb   F  F#   G  *G#  *Gb 
# 110  61  50  64 133    7   3   145  40 119  59  77  13 114    1   10 
length(unique(tonic)) # 16
# should be 12 major scales
```
First convert all essentially same keys to their other name:    
  - C# = Db 
  - Gb = F# 
  - G# = Ab 
  - Cb = B  
so that we have 12 tonics:      
C, Db, D, Eb, E, F, F#, G, Ab, A, Bb, B 
    
```{r}
grep("Cb", unlist(all.chord), value = T) # 164 Cb chords
sum(grepl("B:", unlist(all.chord))) # 7187 B chords
sum(grepl("Gb", unlist(all.chord))) # 1713 chords
sum(grepl("F#", unlist(all.chord))) # 3417 chords
```
Chord annotation: http://ismir2005.ismir.net/proceedings/1080.pdf (see Page 4)
```{r}
length(unique(all_chord)) #???
length(chord.dictionary) # 995 unique chords
```
We want to keep only 4 types of triad chords, theory here http://www.360doc.com/content/11/0301/09/5949657_97283592.shtml 
  
12 maj triads 
12 min triads   
12 dim triads 
12 aug triads 
12 sus triads
= total 60 triads 
    
Solve: minmaj, dim, hdim, aug, sus, digit 
  
1. For minmaj7, theory here http://www.hearandplay.com/main/minor-major-7-chords   
minmaj7 is basically a minor triad.   
Change all chords containing 'minmaj' to '*:min'
```{r}
grep("minmaj", chord.dictionary, value = T)
```
  
2. For dimished chords, theory here http://www.360doc.com/content/11/0301/09/5949657_97283592.shtml  
Change all chords containing 'dim' to '*:dim'
```{r}
grep("dim", chord.dictionary, value = T)
```
  
3. For augmented chords, http://www.360doc.com/content/11/0301/09/5949657_97283592.shtml  
Change all chords containing 'aug' to '*:aug'
```{r}
grep("aug", chord.dictionary, value = T)
```
  
4. For suspended chords, theory here http://www.cndzq.com/bbs/thread-325047-1-1.html  
Change all chords containing 'sus' to '*:sus'
```{r}
grep("sus", chord.dictionary, value = T)
```

5. For ':digit' chords, theory here https://www.youtube.com/watch?v=I0y2LY4sPZA  
Change all chords containing ':digit' to '*:maj'
```{r}
grep("\\:[[:digit:]]", chord.dictionary, value = T)
```

Now stardard chords to roman numbers 1 to 7
https://www.google.com/url?sa=i&rct=j&q=&esrc=s&source=images&cd=&cad=rja&uact=8&ved=0ahUKEwjvyIjXo9HQAhVG64MKHaNsAbIQjRwIBw&url=https%3A%2F%2Fbemusic-guitar.blogspot.com%2F2014%2F10%2Fblog-post_26.html&psig=AFQjCNGhavMaCQTdgQw_1MNGHDmUs04p0g&ust=1480524929775118
```{r}

```

