---
title: "Genre combination"
output: html_notebook
---
###########################################################################
# Notice that wiki_genre is not complete. We need it to be complete first.
###########################################################################
```{r}
with_genre = read.csv("~/Google Drive/Columbia/5243 ADS/ADS Proj 5/Fall2016-proj5-grp2/data/Billboard/with_genre.csv")
sort(table(with_genre$singer_genre), decreasing = T)
# classic rock, soul, country, oldies, 80s, pop, rock, 60s, jazz, disco, rock n roll, blues
```

```{r}
head(with_genre)
sort(table(with_genre$wiki_genre), decreasing = T)
```

Not Found
```{r}
with_genre[grepl("Not Found", with_genre$wiki_genre), 8:9]
with_genre[grepl("Not Found", with_genre$wiki_genre), ]
```

Search for 'Not Found'
```{r}
with_genre[with_genre$id %in% c(1063, 1067, 1069, 1070, 1071, 1078, 1084, 1087, 1099, 1101, 1106, 1110, 1113, 1116, 1118, 1119, 1120, 1123, 1124, 1127, 1132, 1134, 1135, 1145, 1146, 1147, 1149, 1152, 1153, 1154, 1155, 1160, 1166, 1174, 1177, 1188, 1192, 1197, 1200, 1203, 1208, 1221, 1225, 1227, 1235, 1237, 1246, 1247, 1248, 1250, 1253, 1263, 1267, 1269, 1279, 1280, 1283, 1287, 1297), c(8:9, 12:13)]
genre_5 = c("Rock", "Pop", "Pop", "Hard rock", "Rock", "Soul", "Pop", "Folk", "Jazz", "Rock", "Hip hop", "Rock", "Country", "Rock", "Musical/Rmantic", "Rock", "Country", "Country pop", "Rock", "Pop", "Jazz", "Soul", "Country", "R&B", "Folk rock", "Pop", "Jazz", "Rock n roll", "Folk", "Country", "Rock", "Country", "R&B", "Rock", "R&B", "Pop", "R&B", "Rock", "Rock", "Alternative/Indie", "Rock", "R&B", "Country", "Rock", "Funk", "Pop", "Rock", "R&B", "Pop", "R&B", "Pop", "Blues", "Hard rock", "Rock", "Dance pop", "R&B", "R&B", "Country", "Rock")
length(genre_5) # 59
```
c("Rock", "Pop", "Pop", "Hard rock", "Rock", "Soul", "Pop", "Folk", "Jazz", "Rock", "Hip hop", "Rock", "Country", "Rock", "Musical/Rmantic", "Rock", "Country", Country pop", "Rock", "Pop", "Jazz", "Soul", "Country", "R&B", "Folk rock", "Pop", "Jazz", "Rock n roll", "Folk", "Country", "Rock", "Country", "R&B", "Rock", "R&B", "Pop", "R&B", "Rock", "Rock", "Alternative/Indie", "Rock", "R&B", "Country", "Rock", "Funk", "Pop", "Rock", "R&B", "Pop", "R&B", "Pop", "Blues", "Hard rock", "Rock", "Dance pop", "R&B", "R&B", "Country", "Rock")




Country
```{r}
with_genre[grepl("ountry rock", with_genre$wiki_genre), 7:14]
with_genre$Genre[785] <- "Country"
```
Change all *ock to Rock genre
```{r}
sort(table(grep("ock", with_genre$Genre, value = T)), decreasing = T)
with_genre$Genre[grepl("ock", with_genre$Genre)] <- "Rock"
sort(table(with_genre$Genre), decreasing = T)
```
Pop
```{r}
sort(table(grep("(P|p)op", with_genre$Genre, value = T)), decreasing = T)
with_genre$Genre[grepl("(P|p)op", with_genre$Genre)] <- "Rock"

```


