---
title: "Genre combination"
output: html_notebook
---
###########################################################################
# References:
http://musicmap.info/
http://www.musicgenreslist.com/
https://zumic.com/genres/

###########################################################################
```{r}
with_genre = read.csv("~/Google Drive/Columbia/5243 ADS/ADS Proj 5/Fall2016-proj5-grp2/data/Billboard/with_genre.csv")
sort(table(with_genre$singer_genre), decreasing = T)
# classic rock, soul, country, oldies, 80s, pop, rock, 60s, jazz, disco, rock n roll, blues
```

```{r}
head(with_genre)
sort(table(with_genre$wiki_genre), decreasing = T)
```

Not Found
```{r}
with_genre[grepl("Not Found", with_genre$wiki_genre), 8:9]
with_genre[grepl("Not Found", with_genre$wiki_genre), ]
```

Manually search for 'Not Found's actual genre
```{r}
with_genre[with_genre$id %in% c(1063, 1067, 1069, 1070, 1071, 1078, 1084, 1087, 1099, 1101, 1106, 1110, 1113, 1116, 1118, 1119, 1120, 1123, 1124, 1127, 1132, 1134, 1135, 1145, 1146, 1147, 1149, 1152, 1153, 1154, 1155, 1160, 1166, 1174, 1177, 1188, 1192, 1197, 1200, 1203, 1208, 1221, 1225, 1227, 1235, 1237, 1246, 1247, 1248, 1250, 1253, 1263, 1267, 1269, 1279, 1280, 1283, 1287, 1297), c(8:9, 12:13)]
genre_5 = c("Rock", "Pop", "Pop", "Hard rock", "Rock", "Soul", "Pop", "Folk", "Jazz", "Rock", "Hip hop", "Rock", "Country", "Rock", "Musical/Rmantic", "Rock", "Country", "Country pop", "Rock", "Pop", "Jazz", "Soul", "Country", "R&B", "Folk rock", "Pop", "Jazz", "Rock n roll", "Folk", "Country", "Rock", "Country", "R&B", "Rock", "R&B", "Pop", "R&B", "Rock", "Rock", "Alternative/Indie", "Rock", "R&B", "Country", "Rock", "Funk", "Pop", "Rock", "R&B", "Pop", "R&B", "Pop", "Blues", "Hard rock", "Rock", "Dance pop", "R&B", "R&B", "Country", "Rock")
length(genre_5) # 59
save(genre_5, file = "~/Google Drive/Columbia/5243 ADS/ADS Proj 5/Fall2016-proj5-grp2/data/Billboard/genre_5.RData")
```
c("Rock", "Pop", "Pop", "Hard rock", "Rock", "Soul", "Pop", "Folk", "Jazz", "Rock", "Hip hop", "Rock", "Country", "Rock", "Musical/Rmantic", "Rock", "Country", Country pop", "Rock", "Pop", "Jazz", "Soul", "Country", "R&B", "Folk rock", "Pop", "Jazz", "Rock n roll", "Folk", "Country", "Rock", "Country", "R&B", "Rock", "R&B", "Pop", "R&B", "Rock", "Rock", "Alternative/Indie", "Rock", "R&B", "Country", "Rock", "Funk", "Pop", "Rock", "R&B", "Pop", "R&B", "Pop", "Blues", "Hard rock", "Rock", "Dance pop", "R&B", "R&B", "Country", "Rock")



Replace all "Not Found" terms
```{r}
load("/Users/mushroomvv/Google Drive/Columbia/5243 ADS/ADS Proj 5/Fall2016-proj5-grp2/data/Billboard/genre_1.RData")
genre_2 = Max
genre_3 = genre_y$wiki_genre
head(genre_y$wiki_genre)
genre_4 = Cen

NF = c(genre_1, genre_2, genre_3, genre_4, genre_5)
NF[2]
as.vector(NF)
length(NF)

# duplicate 'with_genre' table
final_genre = read.csv("~/Google Drive/Columbia/5243 ADS/ADS Proj 5/Fall2016-proj5-grp2/data/Billboard/with_genre.csv", stringsAsFactors=FALSE)
# final_genre$id[which(with_genre$wiki_genre == "Not Found")][2] # id = 26
# final_genre$wiki_genre[which(with_genre$wiki_genre == "Not Found")][2] <- NF[2]
# final_genre[final_genre$id == 39, 13] # correct

for (i in 1:287) {
  final_genre$wiki_genre[which(with_genre$wiki_genre == "Not Found")][i] <- NF[i]
}
sort(table(final_genre$wiki_genre), decreasing = T) 
sum(table(with_genre$wiki_genre)) # 890
Genre = final_genre[ , -c(1:3,12)]
names(Genre)[9] <- "genre"
head(Genre)

Genre[which(Genre$genre == "[1]"),] # both Rock
Genre[which(Genre$genre == "Brill Building"),] # doo-wop
Genre[which(Genre$genre == "Car song"),] # surf rock
Genre[which(Genre$genre == "Label"),] # Rock, Rock, Jazz, Funk
Genre$genre[which(Genre$id %in% c(25, 27))] = "Rock"
Genre$genre[which(Genre$id == 746)] = "Jazz"
Genre$genre[which(Genre$id == 1201)] = "Funk"
Genre[which(Genre$genre == "Adult contemporary"),] 
Genre[which(Genre$genre %in% c("Hi-NRG", "Jamband", "Lambada", "Merseybeat", "New jack swing", "Power ballad", "Reggae")),] 
# Merseybeat, Power ballad, jamband = Rock
# Reggae, New jack swing, Hi-NRG = R&B
# Lambada = Pop
```

Country includes country and bluegrass
```{r}
Genre[grepl("ountry", Genre$genre), 9]
Genre$genre[grepl("ountry", Genre$genre)] <- "Country"
Genre$genre[grepl("Bluegrass", Genre$genre)] <- "Country"
```

Rock includes all *ock, metal, punk, new wave
```{r}
sort(table(grep("unk", Genre$genre, value = T)), decreasing = T)
Genre$genre[grepl("(P|p)unk", Genre$genre)] <-  "Rock"
Genre$genre[grepl("ock", Genre$genre)] <-  "Rock"
Genre$genre[grepl("metal", Genre$genre)] <-  "Rock"
Genre$genre[Genre$genre %in% c("[1]", "New wave", "Car song", "Adult contemporary", "Merseybeat", "Power ballad", "Jamband")] <- "Rock"
sort(table(Genre$genre), decreasing = T)
```
Pop
```{r}
sort(table(grep("(P|p)op", Genre$genre, value = T)), decreasing = T)
Genre$genre[grepl("(P|p)op", Genre$genre)] <- "Pop"
Genre$genre[which(Genre$genre == "Lambada")] <- "Pop"
sort(table(Genre$genre), decreasing = T)
```

Soul
```{r}
sort(table(grep("oul", Genre$genre, value = T)), decreasing = T)
Genre$genre[grepl("oul", Genre$genre)] <- "Soul"
sort(table(Genre$genre), decreasing = T)
```
Hip-hop
```{r}
sort(table(grep("(H|h)op", Genre$genre, value = T)), decreasing = T)
Genre$genre[grepl("(H|h)op", Genre$genre)] <- "Hip-hop"
sort(table(Genre$genre), decreasing = T)
```
Folk
```{r}
sort(table(grep("olk", Genre$genre, value = T)), decreasing = T)
Genre$genre[grepl("olk", Genre$genre)] <- "Folk"
```

R&B/Soul includes R&B, Soul, Funk, Urban,  
```{r}
sort(table(grep("unk", Genre$genre, value = T)), decreasing = T)
Genre$genre[grepl("(F|f)unk", Genre$genre)] <- "R&B"
Genre$genre[grepl("R&B", Genre$genre)] <- "R&B"
sort(table(grep("isco", Genre$genre, value = T)), decreasing = T)
Genre$genre[grepl("isco", Genre$genre)] <- "R&B"

Genre$genre[Genre$genre %in% c("R&B", "Rhythm and blues", "Soul", "Doo-wop", "Brill Building", "Reggae", "New jack swing", "Hi-NRG", "Dance", "Ska", "House")] <- "R&B/Soul"
sort(table(Genre$genre), decreasing = T)
```

Jazz
```{r}
sort(table(grep("azz", Genre$genre, value = T)), decreasing = T)
Genre$genre[grepl("azz", Genre$genre)] <- "Jazz"
```

Others includes World, Vocal, Latin, Christmas, Holiday, 
```{r}
Genre$genre[Genre$genre %in% c("World", "Vocal", "Latin", "Christmas", "Holiday")] <- "Others"
Genre$genre[grepl("lternative", Genre$genre)] <- "Others" 
Genre$genre[grepl("usical", Genre$genre)] <- "Others"
sort(table(Genre$genre), decreasing = T)
```

Save to final_genre.csv
```{r}
write.csv(Genre, file = "~/Google Drive/Columbia/5243 ADS/ADS Proj 5/Fall2016-proj5-grp2/data/Billboard/final_genre.csv")
```

